Monte Carlo Bootstrap: current developments.

### 2019-04-23 draft.tex
added section on minmin

>>>>

\subsection{Minimum extraction}
Numerical studies pointed to a great hierarchy between $\partial_{\Delta_0} S$ 
and $\partial_{\Delta_l} S$ for $l\geq2$, which explained why the oscillations
for the scalar were much bigger in amplitude than the ones for the higher spin
operators. This motivated using the configuration corresponding to the absolute
minimum of the action instead of averaging over the last 100 or so iterations.

This prescription gave results that were consistently better (had errors smaller
by one order of magnitude). And could be further refined by running an MC
optimization with 0 temperature. (Pending results.)
